Understanding pandoc lua filters

### 2023-08-17 supplement/lua-filters/lua-filters.tex
Updated supplementary materials

function Figure(el)
      local label = ""
      pandoc.walk_block(el,{ Image = function(el)
                     is_fig = 1
                     end})
      if is_fig == 1 then
	        figures = figures + 1
	        label = "Figure " .. tostring(figures) .. ":"
      end
	    local caption = pandoc.utils.stringify(el.caption)
	    if not caption then
          caption = label
    	else
          caption = label .. " " .. caption
    	end
    	el.caption.long[1] = caption
    	is_fig = 0
    	return el
end
\end{verbatim}
\caption{A lua filter to add figure numbering}
\label{code:3}
\end{figure}

@@

\section{Usage of pandoc lua filters in texor package}

\section{Summary}

>>>>

function Figure(el)
      local label = ""
      pandoc.walk_block(el,{ Image = function(el)
                     is_fig = 1
                     end})
      if is_fig == 1 then
	        figures = figures + 1
	        label = "Figure " .. tostring(figures) .. ":"
      end
	    local caption = el.caption
	    if not caption then
          caption = {pandoc.Str(label)}
    	else
          caption = {pandoc.Str(label),pandoc.Space()}
    	end
    	el.caption.long[1].content = caption .. el.caption.long[1].content
    	is_fig = 0
    	return el
end
\end{verbatim}
\caption{A lua filter to add figure numbering}
\label{code:3}
\end{figure}

@@

\section{Usage of pandoc lua filters in texor package}
Pandoc Lua filters are used in texor package to modify the AST for various markups.
 Table \ref{tab:filters} summarizes the use of each filter.
\begin{table}
\begin{tabular}{|l|p{10cm}|}
\hline
File Name & Description\\
\hline
\verb|abs_filter.lua| & {Filters out unicode \verb|182| character.}\\
\hline
\verb|bib_filter.lua| & Clears out bibliography from the article itself as it will added to metadata\\
\hline
\verb|R_code.lua| & Adds a class component \verb|'r'| to CodeBlocks for code highlight \\
\hline
\verb|image_filter.lua| & Fixes extensions for image paths without extension or \verb|.pdf| extension \\
\hline
\verb|table_caption.lua| & Adds Table numbering in the captions similar to the ones found in Rmarkdown and kable based tables. \\
\hline
\verb|image_caption.lua| & Adds Figure/Algorithm/CodeBlock/WideTable numbering as well as clears out residuals of tikz/algorithm images \\
\hline
\verb|conversion_compat_check.lua| & This filter keeps a count all Inline and Block elements and writes it to a yaml file. \\
\hline
\verb|equation_filter.lua| & Adds Bookdown style equation numbering to LaTeX equation/math environments.\\
\hline
\verb|bookdown_ref.lua| & Changes the format of Links to bookdown (markdown) style of links\\
\hline
\verb|issue_checker.lua| & Searches and notifies any occourence of unrecognized math commands.\\
\hline
\verb|find_pdf_files.lua| & This filter creates a list for all Image PDF files included in the article.\\
\hline
\end{tabular}
\caption{A summary of all Lua filters used in texor package (available in \href{https://github.com/Abhi-1U/texor/tree/master/inst}{/inst} folder of package).}
\label{tab:filters}
\end{table}
